---
title: "Lab10"
author: "Yi Wang"
date: "11/20/2018"
output: html_document
---

1. Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.

```{r}
f <- function(q, n, p) {
  if(q >= n)  return(1)  
  else if(q < 0)  return(0) 
  else {
    q <- floor(q)
    sum <- 0
    for(i in 0: q) {
      sum <- sum + choose(n, i) * p^i * (1-p)^(n-i)
    }
  }
  return(sum)
}
  
pbinom(4, 9, 0.8)
f(4, 9, 0.8)
round(pbinom(4, 9, 0.8), 5) == round(f(4, 9, 0.8), 5)
```

2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = ‘one.sample’).

```{r}
p <- function(n, delta, sd, sig.level = 0.05, simulations = 10000){
  x <- replicate(simulations, {
    sample <- rnorm(n, delta, sd)
    pv <- t.test(sample)$p.value
    as.numeric(pv < sig.level)
  })
  power <- sum(x)/simulations
  return(power)
}

power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')
p(n = 30, delta = 0.5, sd = 1)
```

